Hydras \& Co.

### 2023-05-09 doc/chapter-fol.tex
fix a few typos

\begin{remark}
  The constructors of types \texttt{Rel} and \texttt{Fun} are suffixed by an underscore, in order to reserve the names \texttt{a}, \texttt{f}, \texttt{h}, \texttt{R}, etc. to functions which build terms and formulas (please look at Sect~\ref{sec:fol-term-notations} and \ref{sec:fol-atomic-notations}).
\end{remark}

@@

@@

The second language, LNN, is the language of NN (\emph{Natural Numbers}) and has
the same function symbols as LNT plus one relation symbol for less than, LT.

@@

\begin{remark}
  We depart a little from \cite{Goedel}'s notations, where the 
function and relation symbols are called \texttt{Plus}, 
\texttt{Mult}, \texttt{LT}, etc. In our version, these type constructors are called \texttt{Plus\_}, 
\texttt{Mult\_}, \texttt{LT\_}, etc., while the names without final underscores are bound to term building functions (\emph{e.g.}
the function which takes two terms and builds the term representing their sum).
\end{remark}

@@

\begin{todo}
Comment on the use of boths list and sets of formulas.
(explained in Russel's paper, p.7).

\inputsnippets{fol/SystemDef}

\end{todo}

>>>>

\begin{remark}
  \label{rem:underscores}
  The constructors of types \texttt{Rel} and \texttt{Fun} are suffixed by an underscore, in order to reserve the names \texttt{a}, \texttt{f}, \texttt{h}, \texttt{R}, etc. to functions which build terms and formulas (please look at Sect~\ref{sec:fol-term-notations} and \ref{sec:fol-atomic-notations}).
\end{remark}

@@

\subsubsection{Examples}

Let us give the \gallina terms of opur toy language, corresponding to the terms $a$,
$f(a)$, and $h(f(a),a)$. The ``term'' $h(a)$ is not well formed, since the arity of $h$ is not respected.

@@

The second language, LNN, is the language of NN (\emph{Natural Numbers}) and has
the same function symbols as LNT plus one relation symbol for the strict inequality $<$ : \texttt{LT} (less than).

@@

\begin{remark}
  We depart a little from \cite{Goedel}'s notations, where the 
function and relation symbols are called \texttt{Plus}, 
\texttt{Mult}, \texttt{LT}, etc. In our version, these type constructors are called \texttt{Plus\_}, 
\texttt{Mult\_}, \texttt{LT\_}, etc., while the names without final underscores are bound to term building functions (\emph{e.g.}
the function which takes two terms and builds the term representing their sum) (see Remark~\ref{rem:underscores}).
\end{remark}

@@
